Open Data, Open Source and Open Standards in chemistry - The Blue Obelisk five years on

### 2011-04-19 paper.tex
fixed spelling errors

More recently, GGA Software Services (a contract programming company)
released the Indigo toolkit \cite{WebIndigo} and associated software
in 2009 under the GPL. Indigo is written from scratch in C++ and has
high-level wrappers for using it in C, Java, Python, or .NET
environment. Like other toolkits, Indigo provides support for
tetrahedral ans cis-trans stereochemistry, 2D coordinate generation,
exact/substructure/SMARTS matching, fingerprint generation (all these
both for molecules and reactions), and canonical SMILES computation.
It also provides some less common functionality, like matching
tautomers ans resonance substructures, enumeration of subgraps,
finding maximum common substructure of $N$ input structures, and
enumerating reaction products. Indigo also has its rendering plugin,
which is used in a lot of commercial and open-sourse projects as the
main 2D chemical rendering engine.

@@

In the area of cheminformatics tookits, two of the existing toolkits
Open Babel and RDKit are planning to work together on a common
underlying framework called MolCore. This project is still in the
planning stage, but if it is a success it will mean that the the two
libraries will be interoperable (while retaining their existing focus)
but also that the cost of maintaining the code will be shared among
more developers, freeing time for the development of new features.

@@

We hope to see this involvement between the Blue Obelisk and the wider
community grow in future. To this end, we encourage the reader to
visit http://blueobelisk.org, send a message to our mailing list,
investigate related projects or read our blogs.

>>>>

More recently, GGA Software Services (a contract programming company)
released the Indigo toolkit \cite{WebIndigo} and associated software
in 2009 under the GPL. Indigo is written from scratch in C++ and has
high-level wrappers for using it in C, Java, Python, or .NET
environment. Like other toolkits, Indigo provides support for
tetrahedral and cis-trans stereochemistry, 2D coordinate generation,
exact/substructure/SMARTS matching, fingerprint generation (all these
both for molecules and reactions), and canonical SMILES computation.
It also provides some less common functionality, like matching
tautomers ans resonance substructures, enumeration of subgraps,
finding maximum common substructure of $N$ input structures, and
enumerating reaction products. Indigo also has its rendering plugin,
which is used in a lot of commercial and open-source projects as the
main 2D chemical rendering engine.

@@

In the area of cheminformatics tookits, two of the existing toolkits
Open Babel and RDKit are planning to work together on a common
underlying framework called MolCore. This project is still in the
planning stage, but if it is a success it will mean that the two
libraries will be interoperable (while retaining their existing focus)
but also that the cost of maintaining the code will be shared among
more developers, freeing time for the development of new features.

@@

We hope to see this involvement between the Blue Obelisk and the wider
community grow in the future. To this end, we encourage the reader to
visit http://blueobelisk.org, send a message to our mailing list,
investigate related projects or read our blogs.
